We are not the 99 percent: quantifying asphericity in the distribution of Local Group satellites

### 2018-01-22 paper/paper.tex
edits in abstract

\begin{abstract}
We quantify the asphericity in the spatial distribution of the
brightest satellites around the Milky Way (MW) and M31, the dominant
galaxies in the Local Group (LG).
We use the same approach on simulations to build an explicit probability
distribution for this asphericity around galaxies similar to the MW and M31.   
This allows us to estimate the atipicallity
of the satellite distributions in the LG even when the underlying
simulations do not have enough systems that fully resemble the LG.
We demonstrate the method using three different simulations:
Illustris-1,  Illustris-1-DarkMatter and ELVIS. 
We find as a common trends that at most of $1\%$ the pairs are
expected  to have satellite distributions with the same degree of
deviation from sphericity as the Local Group; between $38\%$ to $59\%$
of the pairs have a halo with a satellite distribution as aspherical
as  in M31; and at most $2\%$ have a satellite distribution
as planar as in the MW. 
These results place the LG close to the level of a 3$\sigma$ outlier
in context provided by LCDM simulations.  
\end{abstract}

>>>>

\begin{abstract}
We quantify the asphericity in the spatial distribution of the
brightest satellites around the Milky Way (MW) and M31, the dominant
galaxies in the Local Group (LG).
We use simulations to build an explicit probability distribution for the
asphericity around galaxies similar to the LG in the Lambda Cold Dark
Matter paradigm.
This allows us to estimate the atipicallity
of the satellite distributions in the LG even when the underlying
simulations do not have enough systems that fully resemble the LG.
We demonstrate the method using three different simulations:
Illustris-1,  Illustris-1-DarkMatter and ELVIS. 
We find as a common trends in thse simulations that: i) at most of
$1\%$ the pairs are expected  to have satellite distributions with the
same degree of deviation from sphericity as the Local Group; ii) between
$38\%$ to $59\%$ of the pairs have a halo with a satellite
distribution as aspherical as  in M31; and iii) at most $2\%$ have a
satellite distribution as planar as in the MW. 
These results place the LG close to the level of a 3-$\sigma$ outlier
in context provided by LCDM simulations.  
\end{abstract}
